---
title: "W1 - Make me an interactive map"
author: "Peter Thramkrongart"
output: github_document
---
#### Describe a problem or question in your field for which spatial analysis could be applicable.

Creating emergency evacuation plans for large scale terror attacks or hot-spot city catastrophes such as large explosions.

#### List 5 data layers that you think are necessary to answer your question/solve your problem. Find on the internet github.and then describe examples of two or three of your listed layers.

###### five layers could be:
1:A vector map of roads.  

2:A Vector map of buildings.  

3:An overlay heat map of population density.  

4:Points of suspected terror objectives or vulnerable catastrophe spots.  

5: A Map of building heights.  

A wealth of city maps of roads, buildings, elevations and so on is freely available through Leaflet.  

```{r}
pacman::p_load(pacman,tidyverse, leaflet,htmlwidgets)#load packages
places <- read_csv("RCFeature.csv")#read data
places %>% glimpse()#look at data
```

```{r}
#create a funtion for making labels
labs <- lapply(seq(nrow(places)), function(i) {
  paste0( "<b>","FeatureID: ", places[i, "FeatureID"],'</b><br/>', 
          "FeatureType: ", places[i, "FeatureType"], '<br/>', 
          "Description: ",places[i, "Description"],"<br/>")
})


  #create function for creating a color pallette for coloring markers by the FeatureType

colors <- colorFactor(palette = 'RdYlGn', levels(as.factor(places$FeatureType)))

map <- leaflet() %>% # make leaflet map
  addTiles() %>%
  addMiniMap() %>%
   addMeasure() %>% #add measuring tool
  #add circle markers
  addCircleMarkers(
    data = places,
    lat = ~ places$Latitude,
    lng = ~ places$Longitude,
    color = ~ colors(as.factor(places$FeatureType)),
    popup = places$Description,
    label = lapply(labs, htmltools::HTML),#adding labels as HTML
    clusterOptions = markerClusterOptions(),#cluster close markers
    opacity = 0.95
  ) %>% 
  #add legend for colors
   addLegend('bottomleft', pal = colors, values = as.factor(places$FeatureType),
            title = 'Feature Type',
            opacity = 1)
#save map
saveWidget(map, "map.html", selfcontained = TRUE)

```




